Loop Invariant Code Motion in PyPy's Tracing JIT

### 2011-06-16 talk/iwtc11/paper.tex
add a diagram to show loop peeling. first step in trying to convey they intuition better, more to come tomorrow.
tweak

One of the advantages that tracing JIT compilers have above traditional
method-based
JITs is that their optimizers are much easier to write. Because a tracing JIT
produces only linear pieces of code without control flow joins, many
optimization passes on traces can have a very simple structure. They often
consist of one forward pass through the trace, discarding and replacing
operations in the trace by simpler ones as they walk along it. This makes
optimization of traces very similar to symbolic execution. Many
difficult problems in traditional optimizers become tractable if the optimizer
does not need to deal with control flow merges.

@@

>>>>

One of the advantages that tracing JIT compilers have above traditional
method-based
JITs is that their optimizers are much easier to write. Because a tracing JIT
produces only linear pieces of code without control flow joins, many
optimization passes on traces can have a very simple structure. They often
consist of one forward pass replacing operations by simpler ones or even
discarding them as they walk along it. This makes
optimization of traces very similar to symbolic execution. Also, many
difficult problems in traditional optimizers become tractable if the optimizer
does not need to deal with control flow merges.

@@

\begin{figure}
\begin{center}
\includegraphics[scale=1]{figures/overview}
\end{center}
\end{figure}
